### 2013-06-24 Tex/chapters/model.tex
Kontinuität bei den Fehlerwertangaben
Anmerkung zu k_B = 1 nach vorner verschoben

\subsection{The Disorderd Ising Model}
\label{ssec:isingmodel}
    The used model is a modified 2D Ising model where the \(N=L^2\) sites
    are displaced nodes of a square lattice of edge length \(L\) with
    periodic boundary conditions. The displacement is randomly gauss
    distributed with the standard deviation \(\sigma\). This \(\sigma\)
    is also called \emph{disorder paramter} in the following.
    The hamiltonian of the Ising model is
    \(\hat{H} = \sum_{\avg{i,j}}J_{ij}s_{i}s_{j}\)
    where \(\avg{i,j}\) refers to nodes connected  by edges.
    The edges are constructed according to the in section
    \ref{ssec:graphtypes} defined rules. So that the lattice resembles a
    proximity graph. Each node \(i\) has a spin \(s_i = \pm 1\). Each
    edge has a weight \(J_{ij} = \exp (\alpha (1-d_{ij}))\) with the
    distance \(d_{ij}\) between the nodes \(i\) and \(j\) and
    \(\alpha = 0.5\). \(J\) is called \emph{coupling constant}.\\
    For \(\sigma = 0\) this is the standard Ising model with \(J = 1\),
    for which exists an analytical solution \cite{Onsager1944}.\\

@@

    The searched for property -- the critical temperature \(T_c\)
    -- is only defined for infinite systems, hence every computer
    simulation will show some \emph{finte size effects}.
    %[vielleicht Bild von intensiver Größe?]

@@

    intersect at \(\approx 2.27 k_{B}\). For the sake of simplicity let
    the Boltzmann constant \(k_{B}=1\) in the following.

@@

    gets \(T_c = 2.2689\pm0.0002\), which is in good agreement with the

>>>>

\subsection{The Disordered Ising Model}
\label{ssec:isingmodel}
    The used model is a modified 2D Ising model where the \(N=L^2\) sites
    are displaced nodes of a square lattice of edge length \(L\) with
    periodic boundary conditions. The displacement is randomly gauss
    distributed with the standard deviation \(\sigma\). This \(\sigma\)
    is also called \emph{disorder paramter} in the following.
    The hamiltonian of the Ising model is
    \(\hat{H} = \sum_{\avg{i,j}}J_{ij}s_{i}s_{j}\)
    where \(\avg{i,j}\) refers to nodes connected  by edges.
    The edges are constructed according to the in section
    \ref{ssec:graphtypes} defined rules. So that the lattice resembles a
    proximity graph. Each node \(i\) has a spin \(s_i = \pm 1\). Each
    edge has a weight \(J_{ij} = \exp (\alpha (1-d_{ij}))\) with the
    distance \(d_{ij}\) between the nodes \(i\) and \(j\) and
    \(\alpha = 0.5\). \(J\) is called \emph{coupling constant}.\\
    For \(\sigma = 0\) this is the standard Ising model with \(J = 1\),
    for which exists an analytical solution \cite{Onsager1944}.\\

@@

    The aim of this thesis is to find the critical  temperature \(T_c\)
    of the disordered Ising model in dependece of the disorder parameter
    \(\sigma\). At \(T_c\) the magnetisation \(|m|\) of the system will
    jump and the susceptibility \(\chi_m = \frac{N}{T}\brac{\avg{m^2}-\avg{m}^2}\)
    will diverge. But this behaivior is only present in infinite systems,
    hence every computer simulation will show some \emph{finte size effects}.
    Because of this all through computer simulations observed phase
    transitions will be "smeared out".
    [todo: Bezug zum Bild]
        \subfigure[todo][]
            \label{sfig:smeared_out:meanM}
            \includegraphics[width=0.45\textwidth]{plots/meanM}
        \subfigure[todo][]
            \label{sfig:smeared_out:meanM_L}
            \includegraphics[width=0.45\textwidth]{plots/Mean_M_L_128}
        \caption[]
            todo
        \label{fig:smeared_out}

@@

    intersect at \(\approx 2.27\).

@@

    gets \(T_c = 2.2689(2)\), which is in good agreement with the
